Precise Weed and Maize Classification through Convolutional Neuronal Networks

### 2017-08-18 PaperBCJ.tex

Technological advances have caused industry transformations; manufacturing, food processing, and agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Agriculture of Precision(AP)  which has opened a new field for researching \cite{ortiz2012máquinas}. However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times;  while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer, for the next years it will be planned to introduce some changes concerning to the innovation to improve production \cite{houtart2014desafio}. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects. 
\\

@@

One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by means of infrared (IR) Images. The images were processed by a hysteresis umbral and the Min Neighbouring method to identify the rows of a crop. In recent years the implementation of machine learning has opened new possibilities in weed and crop differentiation process. Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of aplications with noise) \cite{cheng2015feature}. This algorithm demonstrated an effectiveness of 98\% in the identification of rice weeds. Araguez \textit{et. al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image and performed the crop and weed segmentation with unspecified classifiers.
\\

@@

Then, through a first-stage digital image processing procedure, the images were normalized in its green channel. This was done in order to improve green color detection based on the elimination of light and shadow in the images. Later, the green color was extracted from the images to obtain a grayscale equivalent; this was done through the following equation described by Wang, Meng, Luo and Mei \cite{wang2013path}. Following, an OTSU Thresholding was applied to the grayscale images in order to obtain a binary mask. 
\begin{equation}
	S = 2*G - R - B
\end{equation}

@@

It should be noted that samples were manually labeled into two classes; maize and weed, making sure that the images are not repeated. In the following image, final results of the processed images that conform the dataset are shown in Fig. \ref{figure3}.\\

	\begin{figure}[h]
	\centering
	\includegraphics[width=2.5in]{im1}
	\caption{Segmented and Masked images of dataset Above: Weed, Below: Maize}
	\label{figure3}
	\end{figure}

@@

Based on the performance parameters shown in table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was selected; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\

@@

Although results given by this type of network are excellent, one of the main purposes of this paper is the implementation of a real time system. The number of parameters to be computed by the selected network were numerous, so it was necessary to make network modifications in order to improve its processing speed. To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16. This final number of filters used in the network was selected because this is the minimum number of filters that maintain an acceptable training accuracy. The results of the experiment are shown in Table \ref{table:3} \\

\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Comparison between cNET of 16 and 64 filters}
\label{table:3}
\begin{tabular}{|l c c |} 
 \hline
 \textbf{Parameters} & \textbf{cNET 16 filters} & \textbf{cNET 64 filters} \\ [0.75ex] 
 \hline
 Number of parameters & 1651376 & 6421568 \\ 
 Iterations & 9000 & 9000 \\ 
 Accuracy(\%) & 97.26 & 96.40 \\
 Loss(\%) & 8.39 & 14.48 \\ [1ex] 
 \hline 
\end{tabular}
\end{table}

@@

As the table shows, the best results in classification time were achieved by the GPU processor, thus it is the best option to classify a large amount of images. However, this project is thought to be implemented in an autonomous system so the Raspberry Pi was selected for the classification performance analysis due to its portability. The resulting classification time for the cNET of 16 filters was 161 miliseconds, however this time is not optimum for an approximation of real time classification.\\

@@

The results show that for the GPU, classification time has increased by 66\%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, causing some parameters to be computed in the CPU instead of the GPU, thus making the process slower. For the CPU the results are better because the operations are executed using each of the four cores, for this case a decrease in time of 22\% was obtained. Finally, the result for the Raspberry Pi CPU was a time decrease of 6.3 \%.\\

@@

For the estimation of the frames per second for each device, its optimal configuration was considered. The GPU classification time during the test without multithreading was considered for this device. For the CPU and the Raspberry Pi CPU, the results for classification time in the multithreading tests were considered. The devices that showed a realistic number of frames per second are the GPU and the CPU, while the Raspberry Pi CPU did not obtain an achievable rate like it\'s shown in Table \ref{table:6}.\\

\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Test of a complete image and the frames per second}
\label{table:6}
\begin{tabular}[c c c c]{|p{1.1 cm} p{1.7cm} p{1.7cm} p{2.0cm}|} 
 \hline
 \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{Raspberry Pi 3 with Threading} \\ 
 \hline
 Time(s) & 0.0171 & 0.196 & 2.714 \\ [0.95ex]
 FPS & 58.47 & 5.08 & 0.36 \\ [0.95ex]
 \hline
\end{tabular}
\end{table}

@@

The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%. However with the Rasberry Pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably. \\

>>>>

Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Agriculture of Precision(AP)  which has opened a new field for researching \cite{ortiz2012máquinas}. However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times;  while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer, for the next years it will be planned to introduce some changes concerning to the innovation to improve production \cite{houtart2014desafio}. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects. 
\\

@@

One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by means of infrared(IR) images. The images were processed by a hysteresis umbral and the Min Neighbouring method to identify the rows of a crop. In recent years the implementation of machine learning has opened new possibilities in weed and crop differentiation process. Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of aplications with noise) \cite{cheng2015feature}. This algorithm demonstrated an effectiveness of 98\% in the identification of rice weeds. Araguez \textit{et. al} \cite{equipo2006proceedings} implemented a segmentation algorithm through the analysis of the green histogram of the image and performed the crop and weed segmentation with unspecified classifiers.
\\

@@

Then, through a first-stage digital image processing procedure, the images were normalized in its green channel. This was done in order to improve green color detection based on the elimination of light and shadow in the images. Later, the green color was extracted from the images to obtain a grayscale equivalent; this was done through   (\ref{eqn:1}) described by Wang, Meng, Luo and Mei \cite{wang2013path}. Following, an OTSU Thresholding was applied to the grayscale images in order to obtain a binary mask. 
\begin{equation}
\label{eqn:1}
	S = 2*G - R - B
\end{equation}

@@

It should be noted that samples were manually labeled into two classes; maize and weed, making sure that the images are not repeated. In Fig. \ref{figure3}, final results of the processed images that conform the dataset are shown.\\

	\begin{figure}[h]
	\centering
	\includegraphics[width=2.5in]{im1}
	\caption{Segmented and masked images of dataset Above: Maize, Below: Weed}
	\label{figure3}
	\end{figure}

@@

Based on the performance parameters shown in Table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was selected; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\

@@

Although results given by this type of network are excellent, one of the main purposes of this paper is the implementation of a real time system. The number of parameters to be computed by the selected network were numerous, so it was necessary to make network modifications in order to improve its processing speed. To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16. This final number of filters used in the network was selected because this is the minimum number of filters that maintain an acceptable training accuracy. The results of the experiment are shown in Table \ref{table:3}.

\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Comparison between cNET of 16 and 64 filters}
\label{table:3}
\begin{tabular}{|l c c |} 
 \hline
 \textbf{Parameters} & \textbf{cNET 16 filters} & \textbf{cNET 64 filters} \\ [0.75ex] 
 \hline
 Number of parameters & 1651376 & 6421568 \\ 
 Iterations & 9000 & 9000 \\ 
 Accuracy(\%) & 97.26 & 96.40 \\
 Loss(\%) & 8.39 & 13.72 \\ [1ex] 
 \hline 
\end{tabular}
\end{table}

@@

As the Table \ref{table:4} shows, the best results in classification time were achieved by the GPU processor, thus it is the best option to classify a large amount of images. However, this project is thought to be implemented in an autonomous system so the Raspberry Pi was selected for the classification performance analysis due to its portability. The resulting classification time for the cNET of 16 filters was 161 miliseconds, however this time is not optimum for an approximation of real time classification.\\

@@

The results show that for the GPU, classification time has increased by 66\%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, causing some parameters to be computed in the CPU instead of the GPU, thus making the process slower. For the CPU the results are better because the operations are executed using each of the four cores, for this case a decrease in time of 22\% was obtained. Finally, the result for the Raspberry Pi CPU was a time decrease of 6.3\%.\\

@@

For the estimation of the frames per second(FPS) for each device, its optimal configuration was considered. The GPU classification time during the test without multithreading was considered for this device. For the CPU and the Raspberry Pi CPU, the results for classification time in the multithreading tests were considered. The devices that showed a realistic number of frames per second are the GPU and the CPU, while the Raspberry Pi CPU did not obtain an achievable rate like it\'s shown in Table \ref{table:6}.

\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Test of complete image classification in FPS}
\label{table:6}
\begin{tabular}[c c c c]{|p{1.1 cm} p{1.7cm} p{1.7cm} p{2.0cm}|} 
 \hline
 \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{Raspberry Pi 3 with Threading} \\ 
 \hline
 Time(s) & 0.0171 & 0.196 & 2.714 \\ [0.95ex]
 FPS & 58.47 & 5.08 & 0.36 \\ [0.95ex]
 \hline
\end{tabular}
\end{table}

@@

The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%. However with the Raspberry Pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably. \\
